Solent region: Test Maps

### 2021-07-29 Solent_Mapping_v2.Rmd
Added in the section mapping the difference in fuel poverty from 2012 to 2019, this needs chnaging to 2012 and 2018

### Mapping Fuel Poverty
#### 2019 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2021 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2021<-readr::read_csv (inFile)
head(lsoa_fuelpov_2021)
```

```{r Mapping the LSOA 2021 Fuel Poverty}
lsoa_fuelpov_2021$LSOA11CD <- lsoa_fuelpov_2021$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2021_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2021) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2021_merged$pcFP <- as.numeric(lsoa_fuelpov_2021_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2021_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```

>>>>

### Mapping Fuel Poverty
#### 2019 Fuel Poverty
```{r Loading in the LSOA 2021 Fuel Poverty data}
inFile<-paste0(dataFolder, "Fuel Poverty/2019 LSOA_Fuel_Poverty.csv")
lsoa_fuelpov_2019<-readr::read_csv (inFile)
head(lsoa_fuelpov_2019)
```

```{r Mapping the LSOA 2021 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
